\section{previous work}\label{sec:previouswork}
There are flirt apps for smartphones like "myamio - Die Partnersuche für das iPhone" which are used by singles to contact others. Beside flirt apps there are also calendar of events as app-download for enterprising people. A calender of event app is "PRINZ iPhone-App für Veranstaltungen, Bars und Clubs in Ihrer Stadt". This app is for people who mainly want to find a new locality or enterprise, independent of the people who take part. A certain link of calendar of events and flirt app provides the free "Barcardi Togethering App". In this app there is only the possibility to date your own facebook friends but you cannot meet strangers. In contrast to Barcardi app there is no need to join a social network to run ComeTogether app.
What can you do, if you are not interested in relationship and your friends have no time for you but you want to go out and meet some people or you are alone in an unfamiliar environment and want to have an enterprise?
The ComeTogether app is a new and modern way to contact people.
You can meet new people, share common interests and promote sociability.
ComeTogether can reduce barriers of single or lonely people which long for new people.
Moreover, the probability of a disappointment is less if you meet a person with same interests electronically first than you have a face-to-face encounter immediately.
And the electronically way has a certain distance to the unknown people and that gives more security.
ComeTogether is a completely new mixture of calender of events and dating app.
ComeTogether is not limited to a niche like dating apps, which are only made for singles.